An Analysis of the Use of Centipawn Loss to Detect Cheating in Chess

### 2022-11-12 Manuscript/manuscript.tex
added more info to introduction

>>>>

Over the past few months the global chess community has been shaken by a very high-profile story regarding Hans Niemann, Magnus Carlsen, and "alleged cheating" in chess. This "alleged cheating" scandal started when Carlsen withdrew from the Sinquefield Cup, an annual invite-only chess tournament and part of the Grand Chess Tour, after losing to 19-year-old Niemann in a stunning third round defeat.

% Go into detail about why this was such a shock. Include backgrounds of Carlsen and Niemann.

Carlsen didn't immediately stat the reason why he withdrew, in fact at the time he largely stayed quiet. Most people correctly assumed though that Carlsen was holding his tongue in calling out Niemann publicly to avoid a potential reatlitory lawsuit for slander. It should be noted that Carlsen played Niemann again two weeks later in the Julius Baer Generation Cup, but resigned after his second move.

This has become a matter of significant speculation both inside and outside the chess world given the nature of the situation and the people involved.

The first game was played "over the board" (OTB) in contrast to "virtual" chess which is hosted online. Cheating in online chess is very easy. One simply needs to run a chess engine (like Stockfish) and execute the oves from their game into the engine as they played, following up with whichever move it suggested you play next. Cheating OTB is not as simple. Players are commonly required to pass through a metal detector and are not permitted to bring phones or any other elctronic devices with them (see the afore mentioned article about the famous concealed shoe computer).

The specific allegations related to how Niemann cheated OTB are unknown. Also, it would be very hard to prove cheating by simply looking at moves that were made in a single game.
